Analytic reproducibility in articles receiving open data badges at Psychological Science: An observational assessment

### 2020-07-09 manuscript/supplementary_information.Rmd
fixed cross reference bug
osf link adjustments

# Supplementary design and procedures information {#sup_design}

@@

Comparisons between values were partly automated through the use of a custom R function (https://osf.io/teuzb/) that accounted for rounding errors by rounding reanalysis values to the same number of decimal places as original values prior to computing the percentage error and classifying the value as a match, minor discrepancy, or major discrepancy. Note that for `r data_values %>% filter(!is.na(eyeballCheck)) %>% nrow()` values reported relative to a threshold (e.g., p < 0.05) or embedded in figures, we could not directly calculate percentage error and it was necessary to ‘eyeball’ (i.e., visually compare side-by-side) the values to confirm a match.

@@

# Supplementary sample information {#sup_sample}

@@

The first finding encountered in the article that met these eligibility criteria was selected. The target values for the reproducibility checks were a coherent set of descriptive and inferential statistics related to this finding, typically 2-3 paragraphs of information, occasionally accompanied by a table or figure. During this assessment, `r length(noEligibleFinding)` articles were excluded because they did not meet the eligibility criteria (ID codes: `r paste(noEligibleFinding, sep="", collapse = ", ")`). An additional article was excluded because the data no longer appeared to be available (contra Kidwell et al., 2016; ID code: `r dataNoLongerAvailable`). In total, `r data_kidwell_eligible %>% nrow()` eligible articles were identified. A bibliography file is available where article ID codes can be matched to their references (https://osf.io/rszey/). Note that there was a reporting error in our pre-registered protocol which said that article 16-2-2015 was excluded when it was not.

@@

# Supplementary results {#sup_results}

@@

# Supplementary information references {#sup_refs}

>>>>

# Supplementary design and procedures information {#supdesign}

@@

Comparisons between values were partly automated through the use of a custom R function (https://osf.io/mqzj4/) that accounted for rounding errors by rounding reanalysis values to the same number of decimal places as original values prior to computing the percentage error and classifying the value as a match, minor discrepancy, or major discrepancy. Note that for `r data_values %>% filter(!is.na(eyeballCheck)) %>% nrow()` values reported relative to a threshold (e.g., p < 0.05) or embedded in figures, we could not directly calculate percentage error and it was necessary to ‘eyeball’ (i.e., visually compare side-by-side) the values to confirm a match.

@@

# Supplementary sample information {#supsample}

@@

The first finding encountered in the article that met these eligibility criteria was selected. The target values for the reproducibility checks were a coherent set of descriptive and inferential statistics related to this finding, typically 2-3 paragraphs of information, occasionally accompanied by a table or figure. During this assessment, `r length(noEligibleFinding)` articles were not included because they did not meet the eligibility criteria (ID codes: `r paste(noEligibleFinding, sep="", collapse = ", ")`). An additional article was not included because the data no longer appeared to be available (contra Kidwell et al., 2016; ID code: `r dataNoLongerAvailable`). In total, `r data_kidwell_eligible %>% nrow()` eligible articles were identified. A bibliography file is available where article ID codes can be matched to their references (https://osf.io/rszey/). Note that there was a reporting error in our pre-registered protocol which said that article 16-2-2015 was not being included when it was.

@@

# Supplementary results {#supresults}

@@

# Supplementary information references {#suprefs}
